---
title: "Fxns"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(magrittr)
```
## Pipe %>% 
### Ctrl + Shift + M
```{r eval=FALSE}
foo_foo <- hop(foo_foo, through = forest)
foo_foo <- scoop(foo_foo, up = field_mice)
foo_foo <- bop(foo_foo, on = head)
```
vs

```{r eval=FALSE}
foo_foo %>% 
  hop(through = forest) %>% 
  scoop(up = field_mice) %>% 
  bop(on = head)
```

## Functions
###19.2.1
1. because we don't want it to be a parameter that can be changed
all outputs will end up being NA is we set na.rm to false
2. 
```{r}
rescale01 <- function(x) {
  rng <- range(x, na.rm = TRUE, finite = TRUE)
  (x - rng[1]) / (rng[2] - rng[1])
  x[x == -Inf] <- 1
  return(x)
  mean(is.na(x))
}
```
###19.3.1
1. f1 checks to see if the word starts with a certain prefix
could be called is_prefix
f2 wll remove the last element of a vector (remove_last)
f3 gives a vector of length x and repeats y (repeat_max)
3. mvrnorm() returns values from specified normal distribution with multiple variables whereas rnorm() from specified normal distribution with a singular variable
4. by starting them the same, they will both pop up when you type norm_ but that could potentially lead to mistakes and is more work with the _
###19.4.4
1. ifelse requires less code becuase things can be listed easily
2.
```{r}
greeting <- function(){
  h <- lubridate::hour(lubridate::now())
  if (dplyr::between(h, 12, 18)){
    print("Good Afternoon.")
  } else if(dplyr::between(h, 18, 24)){
    print("Good Evening.")
  } else {
    print("Good Morning.")
  }
}
```
```{r}
greeting()
```

3. 
```{r}
fizzbuzz <- function(){
  if (x %% 3 == 0 && x %% 5 == 0){
    print('fizzbuzz')
  } else if (x %% 3 == 0){
    print('fizz')
  } else if (x %% 5 == 0){
    print('buzz')
  }else {
    print(x)
  }
}
```

```{r eval=FALSE}
fizzbuzz(15)
```